Manuscript simulations

### 2023-03-02 Manuscript simulations.Rmd
finished ordination part of simulation

>>>>

```{r}
mat = compas_data[[1]][[1]]$Y
true_coords = compas_data[[1]][[1]]$true_coords
k = 2
sim = 1
niter = 10000
nburnin = 5000
thin = 5
nchains = 3
max_clus = 3
max_attempts = 2

one_sim(
  mat = compas_data[[1]][[1]]$Y,
  true_coords = compas_data[[1]][[1]]$true_coords,
  k = 2, 
  sim = 1, 
  niter = 100000,
  nchains = 3,
  nburnin = 50000,
  thin = 5,
  max_clus = 8,
  max_attempts = 10
)
```
